Visualization of [fulle name] Fractional Integrals

### 2019-04-30 fractional/CMJ style files/article-template.tex
started improving the example section quite a bit, comming together

If we set the value of $\alpha$ to $\frac{4}{5}$, but we do not fix the value of $t$ then Eq.~\eqref{eq:ex1} reduces to:
\begin{equation}
\int_{a_{t}^{\frac{4}{5}}(y)}^{b_{t}^{\frac{4}{5}}(y)} f(\tau)~d\tau 
\end{equation}
If we evaluate the above integral we obtain the area of the region $R_{t}^{\frac{4}{5}}$. The region $R_{t}^{\frac{4}{5}}$ is the region bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{t}^{\frac{4}{5}}(y)$.
Note that $R_{t}^{\frac{4}{5}}$ is a function of $t$. The regions contained in the set $\mathsf{R}^{\frac{4}{5}}$ are depicted in the rightmost panel of Fig\textbf{??}. Let $\mathsf{B}^{\frac{4}{5}}$ contain the right 
edges of the regions contained in the set $\mathsf{R}^{\frac{4}{5}}$. The edges in $\mathsf{B}^{\frac{4}{5}}$ are depicted using different shades of gray. The edges that are associated 
with larger values of $t$ are depicted using lighter shades of gray than those that are associated with smaller values of $t$. Note that b and b are not equal, i.e. altering $t$ will alter 
the shape of the integration strip used  . Changing the value of $t$ alters the shape of the non-rectangular integration strip which is needed

>>>>

Varying both $\alpha$ and $t$ results in Eq.~\ref{eq:ex1}. Eq. can be associated with a multitude of regions. Let $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}=\{R_t^{\alpha}|t\in\mathsf{T},~\alpha\in\mathsf{A}\}$. The regions in the set $\mathsf{R}_{\mathsf{T}}$ 
are depicted in Fig.~\textbf{??}. The regions in Fig that are depicted in the same panel were generated by varying $t$, whilst fixing the value of $\alpha$.

If we set the value of $\alpha$ to $\frac{4}{5}$, but we do not fix the value of $t$ then Eq.~\eqref{eq:ex1} reduces to:
\begin{equation}
\int_{a_{t}^{\frac{4}{5}}(y)}^{b_{t}^{\frac{4}{5}}(y)} f(\tau)~d\tau 
\end{equation}
If we evaluate the above integral we obtain the area of the region $R_{t}^{\frac{4}{5}}$. The region $R_{t}^{\frac{4}{5}}$ is the region bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{t}^{\frac{4}{5}}(y)$.
Note that the shape of $R_{t}^{\frac{4}{5}}$ depends on the value of $t$. The regions contained in the set $\mathsf{R}^{\frac{4}{5}}$ are depicted in the rightmost panel of Fig\textbf{??}. Let $\mathsf{B}^{\frac{4}{5}}$ contain the right 
edges of the regions contained in the set $\mathsf{R}^{\frac{4}{5}}$. The shape of the edges in $\mathsf{B}^{\frac{4}{5}}$ depend on the value of $t$. The edges in $\mathsf{B}^{\frac{4}{5}}$ are depicted in Fig?? using different shades of gray. The shade with which the aformentioned curves are depicted becomes lighter 
as the value of $t$ increases. The two sets b and b are not equal, i.e. the shape of the infinitesimals that make up the regions contained in 
R are dependent on $t$. Although the infinitesimals that make up the regions contained in R have different shapes their form do share common characteristics.

altering $t$ alters the geometric interpretaion of 
Eq???. The shape of the inifinitesimals that make up the region that is associated with Eq depend on the value of $t$.

the shape of the integration strip one has to use to construct the infinite sum that underpins the  used to create the   . Changing the value of $t$ alters the shape of the non-rectangular integration strip which is needed
